Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-11-08 papers/integration/omm_integ.tex
WIP on Reviewer 1's comments, along with a copy of my responses in comments.txt

To the \ccg~model, we added a rate-coded brainstem model (a `saccadic
burst generator') and a biomechanical eye, implemented using the
biomechanical modelling framework OpenSim.  These will be described
below, along with a review of the \ccg~model, but first we will give a
description of the co-ordinate systems and the modelling framework
used.

@@

The generation of the `tonic' phase of the required time series is
achieved simply by integrating the bump over time and multiplying by a
some small gain factor.  This is the function of the tonic neurons
(TNs).  The firing rate of the motor neuron defines the amount of
force applied to the eye by that muscle.  Thus, the size of the `bump'
defines how far the eye moves in that channel's direction.  The gain
and delay parameters in the LLBN-EBN-IBN-LLBN feedback loop therefore
have to be tuned such that the endpoint of the saccade is reasonably
accurate.  Furthermore the restoring force generated by the elasticity
of the muscles is dependent on the radial distance.  The value of the
new tonic firing rate, after the `bump' is dependent on the end
location of the eye.  If the ratio between the EBN firing rate and the
TN firing rate is not exactly correct, the eye will drift away from
the saccade endpoint after the saccade has been completed.  The EBN-TN
connection strength is therefore tuned such that the TN firing rate
yields a stable eye position across a range of eye eccentricities.

@@

We found the best parameters for the exponential in
Eq.~\ref{eq:weightmaps} ($i$ and $j$) by a manual tuning
process. After selecting values for $i$ and $j$ in either the
horizontal or vertical/oblique channels, we ran the model 6 times at
each of 8 target eccentricities (7\dg--14\dg) which were purely in the
direction of the newly parameterised channel. The training saccades
were produced as described below in Sect.~\ref{sec:singlesaccades},
with the same fixation and target luminances (crosses of magnitude 0.2
and 0.3) but with the fixation offset and target onset occurring at
0.2~s. We measured the end-point of the saccade by detecting the
location at which the saccade velocity had dropped below 0.005 of its
peak. We iterated until the mean saccade endpoint plotted versus
target was close to the ideal straight line---see
Fig.~\ref{sacc_vs_targ}(a) \& (c). We applied the same parameters to
both directions of each channel; $i_{up} = i_{down} = 0.00195$,
$j_{up} = j_{down} = 0.075$, $i_{left} = i_{right} = 0.0016$ and
$j_{left} = j_{right} = 0.067$. The resulting weight maps (where the
oblique maps are 1/10$^{\mathrm{th}}$ of the vertical maps, as
described earlier) are shown in Fig.~\ref{weightmaps}.
% From map_modelling2.m:
%    yh=0.0016*exp(0.067.*x);
%    yv=0.00195*exp(0.075.*x);

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=\textwidth]{./figures/weightmaps.png}
\end{center}
\textbf{\refstepcounter{figure}\label{weightmaps} Figure \arabic{figure}.}
{ Weight maps for the connections between the output layer of superior
colliculus and the six long lead burst neurons of the saccadic burst
generator model. Each map increases exponentially with increasing $r$,
multiplied by cosine($\phi$) about its `active' axis. \cmnt{Check
whether Left \& Right are wrong way round}}
\end{figure}

>>>>

To the \ccg~model, we added a brainstem model and a biomechanical
eye model. The rate-coded brainstem model was taken from the
literature~\cite{gancarz_neural_1998} as the best-of-breed saccadic
burst generator~\cite{girard_brainstem_2005}.  The biomechanical eye
was implemented using the biomechanical modelling framework OpenSim.
These will be described below, along with a review of the \ccg~model,
but first we will give a description of the co-ordinate systems and
the modelling framework used.

@@

The generation of the `tonic' phase of the required time series is
achieved simply by integrating the bump over time and multiplying by a
some small gain factor.  This is the function of the tonic neurons
(TNs).  The firing rate of the motor neuron defines the amount of
force applied to the eye by that muscle.  Thus, the integral of the `bump'
defines how far the eye moves in that channel's direction.  The gain
and delay parameters in the LLBN-EBN-IBN-LLBN feedback loop therefore
have to be tuned such that the endpoint of the saccade is reasonably
accurate.  Furthermore the restoring force generated by the elasticity
of the muscles is dependent on the radial distance.  The value of the
new tonic firing rate, after the `bump' is dependent on the end
location of the eye.  If the ratio between the EBN firing rate and the
TN firing rate is not exactly correct, the eye will drift away from
the saccade endpoint after the saccade has been completed.  The EBN-TN
connection strength is therefore tuned such that the TN firing rate
yields a stable eye position across a range of eye eccentricities.

@@

We found the best parameters for the exponential in
Eq.~\ref{eq:weightmaps} ($i$ and $j$) by a manual tuning
process. After selecting values for $i$ and $j$ in either the
horizontal or vertical/oblique channels, we ran the model 6 times at
each of 8 target eccentricities (7\dg--14\dg) which were purely in the
direction of the newly parameterised channel. The training saccades
were produced as described below in Sect.~\ref{sec:singlesaccades},
with the same fixation and target luminances (crosses of magnitude 0.2
and 0.3) but with the fixation offset and target onset occurring at
0.2~s. We measured the end-point of the saccade by detecting the
location at which the saccade velocity had dropped below 0.005 of its
peak. We iterated until the mean saccade endpoint plotted versus
target was close to the ideal straight line---see
Fig.~\ref{sacc_vs_targ}(a) \& (b). We applied the same parameters to
both directions of each channel; $i_{up} = i_{down} = 0.00195$,
$j_{up} = j_{down} = 0.075$, $i_{left} = i_{right} = 0.0016$ and
$j_{left} = j_{right} = 0.067$. The resulting weight maps (where the
oblique maps are 1/10$^{\mathrm{th}}$ of the vertical maps, as
described earlier) are shown in Fig.~\ref{weightmaps}.
% From map_modelling2.m:
%    yh=0.0016*exp(0.067.*x);
%    yv=0.00195*exp(0.075.*x);

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=\textwidth]{./figures/weightmaps.png}
\end{center}
\textbf{\refstepcounter{figure}\label{weightmaps} Figure \arabic{figure}.}
{ Weight maps for the connections between the output layer of superior
colliculus and the six long lead burst neurons of the saccadic burst
generator model. Each map increases exponentially with increasing $r$,
multiplied by cosine($\phi$) about its `active' axis.}
\end{figure}
